|

### 2023-03-24 paper_comparison/paper_comparison/paper_comparison.Rmd
swap the facet such that the x scale is correct

  # Theme
  theme_light() +
  scale_color_manual(values = rcartocolor::carto_pal(4, "Safe")[c(4,1,3,2)]) +
  xlab(expression(log[e] (Effect_size))) +
  ylab("Power") +
  labs(col = "", linetype = "Test") +
  facet_grid(type~conv_or_not, scales = "free_x") +
  theme(legend.position = "bottom")
```

>>>>

  # Theme
  theme_light() +
  scale_color_manual(values = rcartocolor::carto_pal(4, "Safe")[c(4,1,3,2)]) +
  xlab(expression(log[e] (Effect_size))) +
  ylab("Power") +
  labs(col = "", linetype = "Test") +
  facet_grid(conv_or_not~type, scales = "free_x") +
  theme(legend.position = "bottom")
```
